---
title: "Final_UofA_SCProject"
author: "Gavin M. Leighton"
date: "2/22/2015"
output: html_document
---

```{r}
library("ggplot2")
```

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:


The first couple steps allowed me to figure out where I am.

```{r}
setwd("/home/gmleighton/SC_Demo/output/")
CountryData <- read.delim("combined_gapMinder.tsv", sep="\t")
```


I'm going to use Namibia, Botswana, and South Africa so I'm going to use subset to isolate the data from these countries.

```{r}
CountrySubset = subset(CountryData, country == "Namibia" | country == "Botswana" | country == "South Africa")
```

Need to calculate total GDP
CountrySubset$TotalGDP = CountrySubset$pop * CountrySubset$gdpPercap

```{r, echo=FALSE}
FullPlot = ggplot(data = CountrySubset, aes(year,gdpPercap)) + 
  geom_point(size = 3) +
  facet_grid(country ~ .) +
  theme_bw() +
  theme(panel.background = element_rect(colour = "white"), panel.grid.major = element_blank(),
        panel.grid.minor = element_blank())
FullPlot
```



The mean, min, and max of each continent are presented below:

```{r}
ContinentList = as.list(CountryData$continent)
MeanLifeExpectancy = aggregate(CountryData$lifeExp, by = as.list(CountryData$continent), FUN = mean)
```


```{r, echo=FALSE}

```


